GSE74548: Gene Methylation Enrichment Analysis

### 2022-05-11 gmea.Rmd
when there's no FDR sig results

n=50
# effect size median
sig <- subset(gme_res_df,`fdr(selfcontained)` < 0.05)
gs <- head(rownames(sig[order(-abs(sig$median)),]),n)
tstats <- mclapply(gs, function(g) {
  myrows <- which(lapply(gnl,function(x) {
    length(which(x==g))
  } ) > 0 )
  dm[myrows,"t"]
},mc.cores=CORES)
names(tstats) <- gs
tstats <- tstats[order(unlist(lapply(tstats,median)))]
boxplot(tstats,horizontal=TRUE,las=1,
  main="biggest effect size(median)",cex.axis=0.6,
  xlab="t-statistic")
grid()

>>>>

n=50
# effect size median
sig <- subset(gme_res_df,`fdr(selfcontained)` < 0.05)
gs <- head(rownames(sig[order(-abs(sig$median)),]),n)

if ( length(gs) >2 ) {
  tstats <- mclapply(gs, function(g) {
    myrows <- which(lapply(gnl,function(x) {
      length(which(x==g))
    } ) > 0 )
    dm[myrows,"t"]
  },mc.cores=CORES)
  names(tstats) <- gs
  tstats <- tstats[order(unlist(lapply(tstats,median)))]
  boxplot(tstats,horizontal=TRUE,las=1,
    main="biggest effect size(median)",cex.axis=0.6,
    xlab="t-statistic")
  grid()
} else {
  plot(1)
  mtext("too few significant genes found")
}
